Binary companions of red giant stars in \apogee\ \DR

### 2018-03-01 paper/1-catalog/twoface-catalog.tex
Caption

We select a sample of stars that confidently have companions using percentiles
computed from the posterior samples in the velocity semi-amplitude parameter,
$K$.
\figurename~\ref{fig:lnK-percentiles}, shows the distribution of 1st percentiles
of $\ln K$ computed for all stars with posterior samplings from \thejoker\
(filled, blue histogram), along with the same for posterior samplings for the
null control sample (solid line, black).
To select stars with companions, we use a cut in the 1st percentile of the $\ln
K$ samples such that $<1\%$ of the control sample is selected, i.e. our
estimated false positive rate is $<1\%$.
We use a threshold of $\ln K = 0$ to meet this constraint (vertical, dashed line
in \figurename~\ref{fig:lnK-percentiles}); \nhighK\ stars pass this cut.

% Notebook: "Sample K cuts.ipynb"
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{lnK-percentiles}
\end{center}
\caption{%
TODO
\label{fig:lnK-percentiles}
}
\end{figure}

>>>>

We select a sample of stars that confidently have companions using percentiles
computed from the posterior samples in the velocity semi-amplitude parameter,
$K$.
\figurename~\ref{fig:lnK-percentiles}, shows the distribution of 1st percentiles
of $\ln K$ computed for all stars with posterior samplings from \thejoker\
(filled, blue histogram), along with the same for posterior samplings for the
null control sample (solid, dark line).
To select stars with companions, we use a cut in the 1st percentile of the $\ln
K$ samples such that $<1\%$ of the control sample is selected, i.e. our
estimated false positive rate is $<1\%$.
We use a threshold of $\ln K = 0$ to meet this constraint (vertical, dashed line
in \figurename~\ref{fig:lnK-percentiles}); \nhighK\ stars pass this cut.

% Notebook: "Sample K cuts.ipynb"
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{lnK-percentiles}
\end{center}
\caption{%
Distribution of 1st percentiles in $\ln K$ (in units of \kms) for the parent
\apogee\ sample (blue, filled) and for the control sample (solid, dark line).
The vertical line (dashed, orange) indicates our adopted cut to select high-$K$
stars that likely have companions; $<1\%$ of the control sample falls above this
cut.
\label{fig:lnK-percentiles}
}
\end{figure}
